New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/weakschur.tex
Ajout tableau de valeurs WS

>>>>

\subsection{New lower bounds for Weak Schur numbers}
Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The first two inequalities are due to Rowley, they are detailed in [2]. The best lower bound for each integer is highlighted.\\
\\
\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	 & 8 & 9 & 10 & 11 \\
	\hline
	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
	\hline
	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
	\hline
	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
	\hline
	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
	\hline
	\hline
	& 12 & 13 & 14 & 15 \\
	\hline
	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
	\hline
	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
	\hline
	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
	\hline
	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
	\hline
\end{tabular}
\end{center}
With \( S(9) \geqslant 17803 \), we found a new lower bound for
\(WS(10)\) using Rowley's inequality. Moreover, the third inequality
gives new lower bounds for \(WS(9)\) and \(WS(14)\). However, the last
inequality doesn't give any better lower bound, even beyond \( n = 15 \)
: the best bounds are always provided by the first three.
